---
title: "model diagram"
output: html_notebook
---

```{r preloads, include=FALSE}
library(tidyverse)
library(ReDaMoR)
library(jsonlite)
```

Data sets to include as of 19 Sept 2022:

-   Assessors: Parcels
-   BSEED:
    -   Residential Certificates of Compliance
    -   Commercial Certificates of Compliance
    -   Certificates of Occupancy
-   CRIO: Detroit Business Certification Register
-   DAH: Blight Violations
-   DFD: Fire Inspections
-   DHD: Restaurants, [and Inspections, Violations]
-   DPD: Project Green Light Locations
-   OCP: Procurement Agreements
-   LARA: State Licensed Childcare Providers

Data sets to add: - BSEED - Business licenses - Liquor licenses - DWSD: Water bill payment - Treasury: Property Tax Payment Data

```{r assessor_parcels}
# SELECT * FROM parcels_open_data
# LIMIT 1000;
assess_parcels_1000 <- read_csv("Data/parcels_open_data_1000.csv", 
    col_types = cols(object_id = col_character(), 
        taxpayer_2 = col_skip(), property_class = col_character(), 
        homestead_pre = col_character(), 
        is_improved = col_logical(), year_built = col_date(format = "%Y"), 
        sale_date = col_date(format = "%d/%m/%Y"), 
        related = col_character(), subdivision = col_character(), 
        geom = col_character()))

```

```{r bseed_residential_cofc}
# SELECT * FROM active_cofc_final
# LIMIT 1000;
bseed_res_cofc_1000 <- read_csv("Data/active_cofc_final_1000.csv", 
    col_types = cols(issued_date = col_date(format = "%d/%m/%Y"), 
        expire_date = col_date(format = "%d/%m/%Y"), 
        address_id = col_character()))

```

```{r bseed_commercial_cofc}
# SELECT * FROM commercial_inspections_final
# LIMIT 1000;
bseed_comm_cofc_1000 <- read_csv("Data/commercial_inspections_final_1000.csv", 
    col_types = cols(street_num = col_character(), 
        record_status_date = col_datetime(format = "%d/%m/%Y %H:%M:%S")))

```

```{r bseed_cert_occupancy}
# SELECT * FROM certificate_of_occupancy_final
# LIMIT 1000;
bseed_cert_occ_1000 <- read_csv("Data/certificate_of_occupancy_final_1000.csv", 
    col_types = cols(street_num = col_character(), 
        date_status = col_datetime(format = "%d/%m/%Y %H:%M:%S")))

```

```{r dhd_rest_est}
# schema: dbt_dhd_inspections_restaurants
# table: establishments_final : LIMIT 1000
dhd_rest_est_1000 <- read_csv("Data/dhd_rest_establishments_final_1000.csv", 
    col_types = cols(establishment_id = col_character(), 
        zip_code = col_character(), license_number = col_character(), 
        most_recent_license_date = col_date(format = "%m/%d/%Y"), 
        address_id = col_character()))

```

```{r dhd_rest_insp}
# inspections_final
dhd_rest_insp_1000 <- read_csv("Data/dhd_rest_inspections_final_1000.csv", 
    col_types = cols(inspection_id = col_character(), 
        establishment_id = col_character(), 
        inspection_date = col_date(format = "%m/%d/%Y"), 
        inspector_id = col_character(), in_compliance = col_character()))
```

```{r dhd_rest_viol}
# violations_intermediate
dhd_rest_viol_1000 <- read_csv("Data/dhd_restaurants_violations_intermediate_1000.csv", 
    col_types = cols(inspectionid = col_character(), 
        inspectiondate = col_date(format = "%m/%d/%Y"), 
        establishmentid = col_character(), 
        date_corrected = col_date(format = "%m/%d/%Y")))
```

```{r crio_bus_reg}
# SELECT * FROM business_register_final;
crio_bus_reg_all <- read_csv("Data/crio_business_register_final.csv", 
    col_types = cols(business_zip_code = col_character(), 
        business_category_2 = col_skip(), 
        authorized_contact_last_name = col_skip(), 
        lon = col_double(), lat = col_double()))


```

```{r dah_blight}
# SELECT * FROM blight_violations_final
# LIMIT 1000;
dah_blight_1000 <- read_csv("Data/dah_blight_violations_final.csv", 
    col_types = cols(ticket_id = col_character(), 
        violation_street_number = col_character(), 
        violation_zip_code = col_character(), 
        violator_id = col_character(), mailing_address_str_number = col_character(), 
        non_us_str_code = col_character(), 
        country = col_character(), violation_date = col_date(format = "%Y-%m-%d %H:%M:%S"), 
        ticket_issued_time = col_character(), 
        hearing_date = col_character(), hearing_time = col_character(), 
        judgment_date = col_character(), 
        clean_up_cost = col_double(), payment_date = col_character(), 
        collection_status = col_character(), 
        oid = col_character()))

```

```{r fire_inspections}
# SELECT * FROM inspections
# LIMIT 1000;
dfd_inspections_1000 <- read_csv("Data/dfd_inspections_1000.csv", 
    col_types = cols(IO_ID = col_character(), 
        LatestInspDate = col_datetime(format = "%d/%m/%Y %H:%M:%S"), 
        InspWithinLastYear = col_character(), address_id = col_character()))
```

```{r dpd_pgll}
# dpd_project_greenlight_ago
dpd_greenlight_812 <- read_csv("Data/dpd_project_greenlight_ago_812.csv", 
    col_types = cols(precinct = col_double()))

```

```{r ocp}
# ocp_contracts_ago.csv
ocp_contracts_1000 <- read_csv("Data/ocp_contracts_ago.csv", 
    col_types = cols(number = col_character(), 
        amount = col_double(), start_date = col_datetime(format = "%d/%m/%Y %H:%M:%S"), 
        end_date = col_datetime(format = "%d/%m/%Y %H:%M:%S")))

```

```{r lara_childcare}
# schema: dbt_mi_odp_childcare_providers
# tbl: child_care_providers_final
lara_child_455 <- read_csv("Data/child_care_providers_final_455.csv", 
    col_types = cols(capacity = col_integer(), 
        zip = col_character(), address_id = col_character()))

```

```{r id_dataframes}
# model_relational_data()
new_model <- df_to_model(assess_parcels_1000, bseed_res_cofc_1000, bseed_comm_cofc_1000, bseed_cert_occ_1000, dhd_rest_est_1000, dhd_rest_insp_1000, dhd_rest_viol_1000, crio_bus_reg_all, dah_blight_1000, dfd_inspections_1000, dpd_greenlight_812, ocp_contracts_1000, lara_child_455)
```

```{r model_prompt}
# new_model %>%
#    auto_layout(lengthMultiplier=250) %>%
#    plot()
```

```{r}
m <- model_relational_data(modelInput = RelDataModel(list()))
```
